%-------------------------
% Resume in Latex
% Author : Rana Talukdar
% Based off of: https://github.com/Auth0r-C0dez
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{#1 \vspace{-2pt}}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    {\Huge \scshape RANA TALUKDAR} \\ \vspace{1pt}
    \small \href{https://github.com/Auth0r-C0dez}{\faGithub\ GitHub} ~ 
    \href{https://devwithrana.vercel.app/}{Portfolio} ~ 
    +91 8822952024 ~ 
    \href{https://www.linkedin.com/in/rana-talukdar-782b60293/}{\faLinkedin\ LinkedIn} ~
    \href{mailto:kafirana1507@gmail.com}{\faEnvelope\ kafirana1507@gmail.com}
    \vspace{-8pt}
\end{center}

%-----------CAREER SUMMARY-----------
\section{Career Summary}
Building ML and full-stack projects since 2024 with an in-depth understanding of ML-algorithms, GenAI, Neural Networks and MERN. Built multiple ML-models, Computer Vision projects, AI Agents and full-stack projects. ML intern at BlockseBlock. Currently looking for a Full Stack Developer / ML Engineer role.

%-----------SKILLS-----------
\section{Skills \& Interests}
\textbf{Skills:}  ML, LLM, NLP, LangChain, Computer Vision, RAG, NextJS, MERN, SQL, AWS, Docker. \\
\textbf{Soft Skills:} Improviser, Leadership. \\
\textbf{Interests:} Sci-Fi content, Fin-Tech, Cricket, Travelling.

%-----------PROJECTS-----------
\section{Projects}
\resumeSubHeadingListStart

\resumeProjectHeading{\textbf{MailVoyager} $|$ LLM x Full Stack x Automation}{July 2025 -- July 2025}
\resumeItemListStart
  \resumeItem{Developed advanced automation system for sending emails.}
  \resumeItem{Integrated backend using FastAPI.}
  \resumeItem{Fully functional automation system that opens Chrome logs into Gmail account and sends emails based on user requirements.}
  \resumeItem{No API used, all parts of the automation are coded.}
\resumeItemListEnd

\resumeProjectHeading{\textbf{ChatFom} $|$ Full-Stack Developer}{May 2025 -- Present}
\resumeItemListStart
  \resumeItem{Developed advanced chatting platform using MERN.}
  \resumeItem{Integrated VC and audio calling using API calls.}
  \resumeItem{Used JWT for authentication.}
  \resumeItem{Integrated feature for cross-country team members, improving cross-cultural communication skills.}
\resumeItemListEnd

\resumeProjectHeading{\textbf{ISROnautsAI} $|$ ML Engineer}{June 2023 -- July 2024}
\resumeItemListStart
  \resumeItem{Developed a cloud motion prediction model using INSTAT data.}
  \resumeItem{Fused CNN with diffusion model.}
  \resumeItem{Added encoder and decoder for enhancing model performance.}
  \resumeItem{Deployed in Hugging Face with proper working backend.}
\resumeItemListEnd

\resumeProjectHeading{\textbf{Floor-Planning GenAI} $|$ ML Engineer}{Sept 2024 -- March 2025}
\resumeItemListStart
  \resumeItem{Developed a generative AI model for floor planning.}
  \resumeItem{Used diffusion models fused with ControlNET for image enhancement.}
  \resumeItem{Leveraged Flask and Ngrok to deploy the model.}
  \resumeItem{Used augmented data due to lack of data online.}
\resumeItemListEnd

\resumeSubHeadingListEnd

%-----------PUBLICATIONS-----------
\section{Publications}
\resumeSubHeadingListStart
\resumeSubheading
  {A State-of-Art Survey on Generative AI Techniques for Floor Planning}{Sept 2024 -- May 2025}
  {\parbox[t]{0.7\textwidth}{\raggedright \textit{\small Workshop: GenAICHI 2025 – Generative AI and Human-Computer Interaction \\ Conference: CHI 2025 – ACM Conference on Human Factors in Computing Systems}}}{VIT Bhopal University}
\resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
  {Vellore Institue of Technology}{Sept 2023 -- Ongoing}
  {B.Tech in Computer Science and Engineering (AIML)}{Bhopal, India}
  \resumeItemListStart
    \resumeItem{8.33 CGPA, AIML, Web Development, Team Work.}
  \resumeItemListEnd
\resumeSubHeadingListEnd

%-----------EXTRACURRICULAR-----------
\section{Extracurriculars}
\resumeSubHeadingListStart
  \resumeItemListStart
    \resumeItem{Spearheaded and judged a university-wide hackathon, and mentored over 200 participants as a workshop speaker.}
    \resumeItem{Co-lead in two key clubs, driving initiatives in both the technical and R\&D departments.}
  \resumeItemListEnd
\resumeSubHeadingListEnd

\end{document}
